Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-01 progressPresentation.tex
progressPresentation update
Progress presentation update
Progress Presentation update

\begin{frame}{Brake Subsystem}
  \begin{block}{Brake Model}
 \begin{itemize}
        \item System Identification Toolbox
        \item Neural Net Time Series Toolbox
	\end{itemize}

>>>>

\begin{frame}{Brake Subsystem}
  \begin{block}{}
\begin{figure}[H]
  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item All samples within 2\% of the actual output
			\item Transfer function model did not have the same accuracy bounds
			\item Fewer concerns about connections in Simulink
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
  		\end{figure}
